Cover letter for the original IJRR submission

### 2017-09-27 reviews_tro/reviewer_response.tex

\quot{ I also found the description of the environment model being
used,
and the way it is used in planning quite superficial. It is said, that
``an octree data structure'' is used to keep the sampled the
end-effector positions, and it is ``intersect'' with the environment.
The idea is OK, I understand that the octree is a sample-based
representation of the effector's workspace, and using some environment
model it is possible to decide if the given configuration can provide a
contact point or not. but how is the environment described ? How
efficient is this intersection operation ? Does this method require the
environment to be described by some specific objects (e.g. polygons) ?
What about the (unavoidable) uncertainty if a world model acquired via
on-line sensing is considered ? Perhaps some of these issues (e.g.
uncertainty) are not in the scope of the paper, but I can imagine that
a robotic researcher who reads the paper and is about to use the open
source software it advertises is very interested in the answers.}

\as{Thanks for the comment. The choice of not developing too much on the environment description and octree goes along with 
our effort to maintain the paper as readable as possible, since it already contains various concepts. However,
we agree that additional information must be added. We added a Section TODO where we indicate that the environment is represented as a polygon soup (or 3D mesh), and
that we assume that it is fully known. Although the integration of on-line sensing and state estimation in the planner is an issue currently considered by our team, it is indeed
out of the scope of this paper. We thus also indicate that we assume the environment and state of the robot are fully known. We also indicated the algorithmic complexity of the intersection
method to describe how efficient the intersection operation is.}

\quot{I appreciate the thorough presentation of results in the paper, however
it seems that this presentation is somewhat biased towards simulation
results. Simulations are perfectly OK for planning algorithms, but if
you decided to present the experimental results (HRP-2), then at least some
illustrations should be included in the paper. now they are only in the
accompanying video.  also a comparison between the results of the same
task(s) executed in dynamic simulation and on the real robot should
convince the reader that the planning method's good performance does
not depend too much on the idealized simulation environment. }
\as{We agree with the remark, and included some illustrations of the experimental results on HRP-2 in the paper. \\
We now elaborate on the validity of the simulation with respect to an experiment on the real robot. As also suggested by reviewer 1, we added a paragraph
in the paper (TODO where) to provide more information on the simulation we use to validate our motions. This simulation is an implementation of the state of the art approaches used by the community. Of course, it does not guarantee that any motion it validates will be accurately played on the robot, but it is used extensively by the community as a reasonable guarantee of feasibility.  The suggestion of the reviewer to compare the simulation results with those on the real robot is interesting. However, our robot HRP-2 is not torque controlled, but position controlled, therefore as of today a comparison is not possible.}

\section{Answers to reviewer 6}
\quot{ My primary concern, however,
is that the elements described in this paper have been described in
previous published work, which makes the particular contributions of
this work unclear. To be specific, the reachability-guided planner
appears identical to the planner in [20] (as stated by the authors in
the end of Sect. I.B.), and the optimal control formulation is from [1]
(again as stated in I.B.).}
\as{Thanks for the comment. Indeed, all reviewers agreed that the contribution with respect to previous work was not clearly stated. We updated the paper to reflect the following. Firstly, our planner is almost identical to the one in [20], with important additions that are the pseudo code for the algorithm (the algorithm is not given in [20]), as well as the introduction of a more efficient criterion
for checking static equilibrium (see next question). The optimal control is no longer a claimed contribution of the paper, even though it differs from [1] in its formulation. The main
novelty of the paper resides in the experimental setup and analysis, as well as the empirical proof that the planner works with real robots that are more constrained kinematically than the virtual avatars from [20]. We believe that this paper is thus in accordance with the guidelines of T-RO regarding the extension of a conference paper.}

\quot{The authors highlight a particular
contribution of this work to be the efficient robust balance criterion,
but I had trouble understanding this particular contribution. Does this
refer to the approximation of equilibrium feasibility by contact
reachability? In that case, how does this differ from just applying the
planner in [20] directly? Or does this refer to the robustness
parameter $b_0$ in Appendix B Eq. (15)?}
\as{Indeed, this part was also not clear. The robust balance criterion (renamed equilibrium criterion) indeed refers to the parameter $b_0$ in Appendix B. The solved
LP replaces the static equilibrium test performed in [20], which was not computationally efficient, and took up to 4ms per candidate to compute. We updated the paper to explain
this in details.}

\quot{In addition, sections IV and V are very similar to the description of
the planner in [20]. That's not surprising, of course, but there is no
indication in those sections that the work being presented is a
rephrasing of an earlier publication.[\dots] }
\as{We agree with the comment, and indeed made this clearer in the new submission.}

\quot{I do, however,
believe that the fact that the technical approaches are rephrasings of
prior work should be made more clear (or that sections which can be
replaced by citations of [20] and [1] be removed).}
\as{Thanks for the advice. This suggestion was in contradiction with the other reviewers, who thought that the paper should be self-contained.
The associate editor decided that the paper must be self contained, so we maintained the indicated sections, but made clearer the fact that they are rephrasing of previous work. }

\quot{*I think I understand what the authors mean by solving at
"interactive" rates, but this is worth defining. In my mind, it means
something like "before the human operator gets bored", or roughly > 0.5
Hz. But since the authors make the claim that this is the "first
interactive implementation of a contact planner", then that statement
should be made quantitative and verifiable}
\as{We agree with the relevant comment, and updated the paper accordingly.}

\quot{* In Section I.A. the authors refer to Bretl's work on multi-contact
planning as the inspiration for the P1,P2,P3 decomposition of the
problem. But it is not, as the authors state, always necessary to
decompose motion planning into choosing a series of quasi-static
configurations. There are a variety of feasible motions with no static
equilibrium configurations, so it is worth mentioning that this
decomposition only solves a subset of motion planning problem.}
\as{We apologize if this was not made clear enough in our first submission. In the conclusion, we indicate that the planner is limited to specific scenarios (where quasi-static motion
is always an option). We updated the state of the art to indicate that the decomposition in general is restricitve.}

\quot{* Also in Sect. I.A, the authors state that "optimization-based
approaches only converge locally". This is not necessarily true, as
convex or mixed-integer convex optimizations can (sometimes) be solved
to a verifiable global optimum. I would suggest removing this sentence
entirely.}
\as{Thanks for the suggestion. Our phrasing was indeed misleading and inaccurate. Our intention was to explain that the geometry of the scene make the problem highly non-convex, and
that approaches such as the CIO, if not initialized with an appropriate initial guess, might never get out of the local minima. We followed the reviewer's advice and simply removed the sentence. }

\quot{* I am not sure why the $C_{reach}$ hypothesis is described as the ``strong''
hypothesis in, e.g., Sect. IV. Is there a corresponding weak
hypothesis?}
\as{We apologize for the confusion, that comes from a inaccurate use of English by the main author. What we meant was that the hypothesis is TODO}

\quot{* In Sect. IV.B, the authors state that the ideal shape $B^*$ ``has no
explicit definition''. For a particular configuration  $q_0$, $B^*$ is simply
the surface of the robot, right? So I assume that this claim refers to
there being no explicit definition of B* which is the volume around
$B^*(q_0)$ for every $q_0$? I think I agree with the authors, but I found
this claim hard to follow and would appreciate some clarification}
\as{We updated the Section IV B. to better explain our claim. Indeed, as the reviewer states $B^*$  is the volume for every $q_0$. If such a volume existed, we would know exactly whether or not a given root configuration can result in a valid contact configuration.
We of course doubt that $B^*$ actually exists. }

\quot{* In Sect. V.A., the authors mention that the ability to plan a contact
break and creation with the same limb allows the creation of dynamic
motions. This is quite an important ability for an otherwise
quasi-static planner, but this ability isn't described again until the
appendix. It would be worth explaining why this is true in the paper
itself. }
\as{Thanks for the suggestion. We added a paragraph to better explain this in Section V.A.}

\quot{In Sect. V.B, the authors mention inserting an additional state
between contact configurations if two or more contacts cannot be
maintained. Shouldn't this step appear somewhere in Alg. 1?}
\as{We apologize for the lack of clarity. This is actually handled by the method \textsc{RepositionContacts}. We now realize that the name is misleading. Indeed,
\textsc{RepositionContacts} either adds a new contact, or tries to reposition one already existing. In Appendix D, we state:
\textit{Otherwise, the method \textsc{RepositionContacts} is called. It repositions one end effector (either a free
limb, or the oldest active contact) towards a new contact
position if possible. }

We changed the name to \textsc{TODO}, with the hope that it makes things clearer.}

\quot{* In Appendix A.A, it is mentioned that step 2 in the workspace
computation is conservative, with reference to figure 17-right. But
Fig. 17-right is the simplification of the convex hull, corresponding
to step 3, and it's actually hard to tell from the figure that it is
conservative. Not knowing anything about Blender's decimate tool, I
assume it is operating by removing vertices, which would indeed be
conservative, but some clarification would be useful here.}
\as{Indeed, the decimate tools removes vertices, and this was not explained clearly in the paper. We updated the text accordingly}

\quot{* Finally, I would suggest providing explicit git SHAs or tags for all
of the github links. I've personally made the mistake of linking to a
github project in a paper, only to have that project change and
eventually delete the specific code I was citing. }
\as{The reviewer is absolutely right. We indeed encounter the issue with other researchers that are currently using our planner. 
To address this issue, the link for the code now points at a website, where instructions are given to install the correct version of the project.
Regarding the link to the python code for the OCP that addresses P3, we provided an explicit git SHAs, as suggested by the reviewer.}

\end{document}
